---
title: 'Package Presentation: MAGICK'
author: "OJO SEGUN ADEWALE"
date: "20 June 2018"
output:
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
library("magick")
library("knitr")
```

## An Overview

- Description, An open source software 

     + Author: Jeroen Ooms 

     + Maintainer: Jeroen Ooms        

     + Repository: CRAN

     + Date/Publication: 2018-05-11 20:09:05 UTC
     
     + E-mail: jeroen@berkeley.edu


## Introduction....

What is Magick?

   - Basically an open source animation software package
      
   - Tools that can be used to read, write, and manipulate images 
     
     in almost any format including TIFF, JPEG, PNG, PDF, photoCD
     
     and GIF.
    
    
## Basic characteristics

   - Reads image directly from a file path, URL, or raw vector with            image data

   - Automatically converts and renders all common image formats
 
   - Images are automatically previewed when printed to the console,           resulting in an interactive editing environment.
   
   - You can also save with the pipe functions; image_charcoal(eagle) %>%   
     image_write ("E:/Rpackageprsentation/testing3.png")

   


## Downloading image from the internet

```{r,echo=TRUE}
#read image
eagle <- image_read("https://i0.wp.com/eagle-science.org/wp-content/uploads/2015/10/eagle_test.png")
#https://i0.wp.com/eagle-science.org/wp-content/uploads/2015/10/eagle_test.png
print(eagle)
```

## Function: Image Transform
```{r,echo=TRUE}
image_trim(eagle)
```

## Function: Image Transform
```{r,echo=TRUE}
image_flip(eagle)
```

## Function: Image Transform
```{r, echo=TRUE}
image_negate(eagle)
```

## Function: Image Attribute

```{r,echo=TRUE}
image_comment(eagle, comment = NULL)
image_info(eagle)
```

## Function: Image Colour
```{r,echo=TRUE}  
#adding background colour
eagle %>% 
  image_background("green") %>% 
  image_flatten() %>%
  image_border("red", "10x10")
```

## Function: Image Colour
```{r,echo=TRUE}
#To plot and export apart from writing the code
x<-eagle %>% 
  image_background("green") %>% 
  image_flatten() %>%
  image_border("red", "10x10")
plot(x)
#write image and it will automatically save it in the specified folder
image_rotate(eagle, 1) %>% image_write("E:/Rpackageprsentation/testing1.png")
image_rotate(x, 1) %>% image_write("E:/Rpackageprsentation/testing2.png")
```

## Function: Image Special Effect

```{r,echo=TRUE}
  image_oilpaint(eagle)
```

## Function: Image Special Effect
```{r,echo=TRUE}
  image_charcoal(eagle) 
```

## Function: Image Special Effect
```{r,echo=TRUE}
  image_edge(eagle)
```

## Function: Image Special Effect
```{r,echo=T}
image_noise(eagle, noisetype = "gaussian")
```

## Function: Image to ggplot

```{r,echo=TRUE}
#Plot with base R plotting magick using ggplot
#convert image to raster
   image_raster(eagle, frame = 1, tidy = TRUE)
  image_ggplot(eagle)
```

## Function: Image to ggplot
```{r,echo=TRUE}
image_ggplot(eagle)
```

## Function: Image to ggplot2
```{r,echo=TRUE}
library("ggplot2")
  myplot <- image_ggplot(eagle)
  myplot + ggtitle("Explore species-environment interaction")
```

## Function: Image frames and Animation
```{r,echo=TRUE}
 #Download/read first image
  nn<- image_read("E:/Rpackageprsentation/style2/img_nnet.jpg")
  image_trim(nn)
```


## Function: Image frames and Animation
```{r,echo=TRUE}
#Download/read second image
  rf<- image_read("E:/Rpackageprsentation/style2/rfplot.png")
  image_trim(rf)
```

## Function:  Image frames and Animation

```{r,echo=TRUE}
  compare <- c(nn, rf)
  compare <- image_scale(compare, "400x400")
#create morphine animation
  (animation1 <- image_animate(compare))    #This is too fast
  image_write(animation1, "E:/Rpackageprsentation/testing4.gif")
```

## Function:  Image frames and Animation

```{r,echo=TRUE}
#Morph effect  <--- Quite steady
  (animation2 <- image_animate(image_morph(compare, frames = 20)))
```

## Conclusion

  This is another medium of animation that can be carried out in 
  
  R which is quite more interesting to explore.
 
 
  
  For further analysis and information about this package
 
  https://cran.r-project.org/web/packages/magic/index.html



  Thank you all for  your time
